### 2016-01-20 paper.tex
Last of @nearyvs suggestions; resolves #46

The wake at $x/D=0.93$ downstream was shown to be relatively symmetrical and
lacked the evidence of strong blade stall, which once again differentiates this
turbine from the UNH-RVAT. Terms from the mean kinetic energy transport equation
were also computed in this $y$--$z$ plane, showing the relative importance of
the vertical advection compared with turbulent transport terms at this location.
It is interesting to note that though the RM2 is a more effective energy
converter than the UNH-RVAT, its wake recovery may in fact be slower due to
weaker blade tip vortex shedding and lower levels of turbulence in the
near-wake.

This data, along with the code for processing and visualization, is provided
openly via a Creative Commons license (MIT license for code), and is available
as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
citeable archive \cite{Bachant2015-RM2-data}. The authors hope that this can
provide opportunities for extensive validation of predictive tools for the
complex unsteady flow physics of cross-flow turbines.

>>>>

While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
evidence of strong blade stall, both of which differentiate this near-wake from
the higher solidity, lower optimal $\lambda$ UNH-RVAT. Terms from the mean
kinetic energy transport equation were also computed in this $y$--$z$ plane,
showing the relative importance of the vertical advection compared with
turbulent transport terms at this location. It is interesting to note that
though the RM2 is a more effective energy converter than the UNH-RVAT, its wake
recovery may in fact be delayed due to weaker blade tip vortex shedding and
lower levels of turbulence in the near-wake.

This dataset, along with the code for processing and visualization, is provided
openly via a Creative Commons license (MIT license for code), and is available
as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
citeable archive \cite{Bachant2015-RM2-data}.
